\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{xcolor}
\definecolor{MyBlue}{rgb}{0.25,0.7,0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{MyBlue}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{\LARGE BIDHOV BIZAR} \\

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
\hline
\textbf{Examination} & \textbf{University} & \textbf{Institute} & \textbf{Year} & \textbf{CGPA/\%} \\
\hline
Post Graduation \,\, & \textit{Electrical Communication Engineering} \\
 & IISc Bangalore & IISc Bangalore  & 2021 & 6.5 \\
Graduation & \textit{Electronics Engineering} \\
 & MG University, Kottayam & RIT, Kottayam & 2016 & 7.52\\
A.I.S.S.C.E. & CBSE& K V No 2, Kasaragod & 2012 & 94.0 \\
A.I.S.S.E & CBSE & K V No 2,Kasaragod & 2010 & 9.2 \\
\hline
\end{tabular}
%\end{center}
%\end{table}
\\ \\

\resheading{\textbf{RESEARCH INTEREST} }\\[\lsep]
\begin{itemize}
\item \noindent Distributed Network Inference and Tracing
\item \noindent Machine Learning , Detection and Estimation Theory , Communication Network
\end{itemize}

\resheading{\textbf{EXPERIENCE} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Summer Intern - ROBOSAPIENS -  Jne'15  to  July'15:} \\
\textbf{Detailed study of ATMEGA328 , ATMEGA168: } Implementation robotic arm with 2 degree of freedom using single MCU.

\textbf{Linux from Scratch:}
Project  dealt  with  creating a new OS for clients of CoolMinds Inc..  Analysing  and  resolving  production  issues,  processes  using shell scripting.

\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Languages: } C, C++, Java , Python
\item \noindent \textbf{Tools: } mikroC , \LaTeX, Google Colab, JTAG, MATLAB , NS3, Kafka .
\item \noindent \textbf{Machine Learning Libraries:} TensorFlow, Scikit-learn , Pandas 
\end{itemize}

\resheading{\textbf{PROJECTS} }\\[\lsep]


\begin{itemize}\itemsep \isep
\item \textbf{Comparative study of various Multi-label Regression techniques:} Implemented linear regression,logistic regression, matrix sketching,xgboost regression, Random forest Regression . Compared the performance on a multi-target dataset.

\item \textbf{Implemented NS3:} Implemented basic NS3 flow simulation to analyze flow congestion. Visualized the network connection using simnet.

 \item \textbf{Kafka Implementation :} .
 Implemented Kafka to analyze the leader selection protocol for multiple broker system.
 
\item \textbf{Multi-label binary Classification: } Implemented Naive Bayes classifier to predict the number of trump cards from output set of five labels, marking each output label as 1 if the label works as trump card otherwise 0.

\item \textbf{Gravitational Waves :} Helped in analyzing gravitational waves in workshop done in CUSAT,Kerala.

\end{itemize}

\textbf{MAJOR PROJECTS :}
\begin{itemize}\itemsep \isep
\item \textbf{ Intelligent Heterogenous Traffic Analyzer:} Its a traffic analyzer tool that takes input from the sheet of sensors placed on 4 way junction strategically. The projects aim is to overcome the hurdles of camera. The device is placed in a traffic junction which would report the vechile class , vehicle density , average flow speed.

\item \textbf{Blind E Book Reader:} A general purpose device that helps the blind to read braille without using the braille print. The device uses actuators that print the braille letter on the skin of the user at variable speed and punctuation that makes the experience more lively.
The projected was short listed in (AIYEHUM 2015 )IEEE.

\item \textbf{Bio Plant Automation :} Under Tropical Institute of Ecological Science, Kottayam a bio gas plant for commercial use was required to be designed. The design required the temperature,moisture and other parameters to be in check within the plant for research purpose.

\item \textbf{INMO Camp 2011-2012 :} Had to attend the INMO training camp as i qualified the JMO 2010.
\end{itemize}


\resheading{\textbf{ACHIEVEMENTS} }\\[\lsep]
\begin{itemize}
\item \noindent AIR 1276 in GATE 2018
\item \noindent RANK 1997 in KEAM 2012
\item \noindent RANK 99 in JMO 2010
\end{itemize}


\end{document}